\textbf{Measuring Depression and Anxiety with 4 items? Adaptation of the PHQ-4 to increase its Sensitivity to Subclinical Variability}

### 2025-06-09 paper/5_Collabra/manuscript.tex
add response file

\authornote{\par{\addORCIDlink{Dominique
Makowski}{0000-0001-5375-9967}}\par{\addORCIDlink{An Shu
Te}{0000-0002-9312-5552}}\par{\addORCIDlink{Ana
Neves}{0009-0006-0020-7599}}\par{\addORCIDlink{S.H. Annabel
Chen}{0000-0002-1540-5516}} 
\par{ }
\par{     \begin{tcolorbox}[enhanced jigsaw, left=2mm, opacityback=0, rightrule=.15mm, leftrule=.75mm, arc=.35mm, breakable, colframe=quarto-callout-note-color-frame, bottomrule=.15mm, colback=white, toprule=.15mm]

>>>>

\authornote{\par{\addORCIDlink{Dominique
Makowski}{0000-0001-5375-9967}}\par{\addORCIDlink{An Shu
Te}{0000-0002-9312-5552}}\par{\addORCIDlink{Ana
Neves}{0009-0006-0020-7599}}\par{\addORCIDlink{S.H. Annabel
Chen}{0000-0002-1540-5516}} 
\par{ }
\par{     \begin{tcolorbox}[enhanced jigsaw, breakable, bottomrule=.15mm, colback=white, opacityback=0, arc=.35mm, leftrule=.75mm, rightrule=.15mm, left=2mm, toprule=.15mm, colframe=quarto-callout-note-color-frame]
